---
title: "P136558_LiuXiaotian_Assignment1"
author: "Liu_Xiaotian"
date: "2024-04-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analysis of Women's Clothing E-Commerce Dataset

## 1. Introduction

Introduction:

In the fast-paced world of e-commerce, customer feedback serves as a cornerstone for shaping consumer decisions and driving business success. The Women’s Clothing E-Commerce dataset presents a valuable repository of customer reviews, offering profound insights into consumer preferences and sentiments within the online fashion retail landscape.

Comprising 23,486 rows and 10 feature variables, each representing a unique customer review, this dataset encapsulates essential attributes such as Clothing ID, reviewer Age, Title and Text of the review, Rating (ranging from 1 to 5), and a Binary indicator of product recommendation. Additionally, variables documenting Positive Feedback Count and categorical attributes like Division Name, Department Name, and Class Name provide further context into product divisions, departments, and classes.

This dataset's real-world relevance lies in its authenticity, reflecting genuine commercial data sourced from an e-commerce platform. While ensuring privacy and anonymity by replacing company references with a generic term, "retailer," the dataset offers ample opportunities for text analysis. Its nine supportive features enable exploration across multiple dimensions of customer feedback.

In this report, we embark on analyzing this dataset to unearth valuable insights into customer behavior, product performance, and overall sentiment within the realm of women's clothing e-commerce. While our analysis may not include correlation analysis, regression analysis, or machine learning techniques, our aim remains to extract meaningful patterns and trends that can guide business strategies, elevate customer satisfaction, and foster innovation in the online fashion retail sector.

## 2. Analysis Process

### a) Data Pre-processing:

Before proceeding with the analysis, it's essential to preprocess the data to ensure data quality and accuracy. Data pre-processing typically involves steps such as data loading and data sampling.

```{r}
library(dplyr)
library(tidytext)
library(ggplot2)

setwd('/Users/liuxiaotian/Documents/P136558_LiuXiaotian_DataManagementAssignment1')
data <- read.csv('Womens Clothing E-Commerce Reviews.csv')
str(data)
set.seed(123)
sample_data <- data[sample(nrow(data), 500), ]
str(sample_data)
```

### b) Basic Analysis:

For basic analysis of the dataset, start by generating summary statistics using the summary() function to understand the numeric variables' distribution and central tendencies. Next, explore the unique values of categorical variables like ratings and department names using the unique() function to grasp the dataset's categorical structure. Visualize the distribution of important variables such as age using histograms and understand the frequency of ratings through barplots. Additionally, calculate the average rating for each clothing item by grouping the data by Clothing ID and sorting the ratings to identify top-rated items. Visualize these ratings using barplots with distinct fill colors representing different rating ranges. This basic analysis provides initial insights into the dataset's characteristics, enabling further exploration and analysis.

```{r}
summary(sample_data)
```

The summary of the `sample_data` reveals several key insights about the dataset. Reviewers span a wide age range, with the majority falling between 34 and 52 years old. Ratings are predominantly positive, with most falling within the 4 to 5 range. Additionally, a significant portion of reviewers recommends the products, indicating satisfaction. The count of positive feedback per review is generally low, suggesting that most reviews receive minimal additional validation. The dataset encompasses various product divisions, departments, and categories, providing ample opportunities for further analysis to uncover patterns and trends within customer demographics and product preferences.

```{r}
unique(sample_data$Rating)
unique(sample_data$Recommended.IND)
unique(sample_data$Division.Name)
unique(sample_data$Department.Name)
unique(sample_data$Class.Name)
```

From the data, we can derive that ratings range from 1 to 5, with recommendation indicators of 1 and 0. There are four product divisions and over 20 product classes represented in the dataset.

By generating the histogram titled "Distribution of Age" with "Age" on the x-axis, we aim to visually understand the spread and frequency distribution of reviewers' ages in the dataset. The histogram provides insights into the age demographics of the reviewers, such as the central tendency, spread, and any potential outliers.

From the histogram, we observe that the age distribution of reviewers covers all age groups from 0 to 100 years old, but it is primarily concentrated between 20 and 70 years old. Specifically, the highest frequencies are observed in the age ranges of 30-40, followed by 40-50, 50-60, 20-30, and 60-70. This indicates that middle-aged individuals are the primary reviewers in the sample data, with significant participation from younger and older age groups as well. Therefore, these insights help provide a comprehensive understanding of the age characteristics of the reviewers and offer valuable guidance for marketing strategies and product positioning targeting different age groups.

```{r, echo=FALSE}
hist(sample_data$Age, main = "Distribution of Age", xlab = "Age")
```

By generating a bar chart titled "Count of Ratings" with "Rating" on the x-axis, the aim is to visually understand the distribution of frequencies for each rating level in the dataset. The bar chart provides a quick overview of the quantity of each rating level, offering insights into the overall evaluation trends of reviewers towards the products.

Based on the distribution of rating levels, we observe an exponential increase in the quantity of ratings from low to high levels. Specifically, the quantities of ratings 1 and 2 are the lowest, while the quantity of ratings 3 is approximately twice that of ratings 2. Similarly, the quantity of ratings 4 is approximately twice that of ratings 3, and the quantity of ratings 5 is approximately twice that of ratings 4.

These findings indicate that the majority of reviewers have given positive evaluations of the products, as the quantity of high ratings significantly outweighs the quantity of low ratings. However, further analysis of the specific content behind each rating level is needed to understand the reasons and trends behind the evaluations. Additionally, this suggests that while the overall product quality is high, there may still be room for improvement to further enhance customer satisfaction and product reputation.

```{r, echo=FALSE}
barplot(table(sample_data$Rating), main = "Count of Ratings", xlab = "Rating")
```

By creating this frequency table, we aim to understand the distribution of reviews across different product departments. The output shows the number of reviews associated with each department category, including "Bottoms," "Dresses," "Intimate," "Jackets," "Tops," and "Trend."

Insights can be gained by identifying which departments receive the most reviews and which receive the least. For example, "Tops" has the highest count of reviews with 224, followed by "Dresses" with 136 reviews. On the other hand, "Trend" has the lowest count with only 6 reviews. This information can help in assessing the popularity and focus of different product departments within the retailer and guide decision-making related to inventory management, marketing strategies, and customer engagement efforts.

```{r}
table(sample_data$Department.Name)
```

Now, I'm going to calculate the average rating for each clothing item and visualize the results in a bar chart.

Firstly, the group_by() and summarise() functions are used to compute the average rating for each clothing item, and the results are stored in the average_rating data frame.

Next, the arrange() function is applied to sort the average_rating data frame in descending order based on the average rating, facilitating the identification of the top-rated items.

Then, the head() function is used to extract the top ten items with the highest average ratings, and the results are stored in the top_items data frame.

Subsequently, the average_rating data frame is processed to categorize the average ratings into different ranges using the cut() function, and the results are stored in the rating_range column.

Finally, the ggplot() function is utilized to create a bar chart where the x-axis represents the clothing item identifiers, the y-axis represents the average rating, and the fill color of the bars represents different rating ranges. Additionally, the scale_fill_manual() function is employed to specify the mapping of fill colors to different rating ranges. The labs() function is used to set the title and axis labels of the chart, while the theme() function adjusts the angle and position of the x-axis labels within the bar chart.

By executing the above code, we obtain insights into the average ratings of each clothing item and visually represent the distribution of these ratings in the form of a bar chart. Furthermore, we can identify the top-rated items and further analyze the distribution of rating ranges to gain deeper insights.


```{r, echo=FALSE}
average_rating <- sample_data %>%
  group_by(Clothing.ID) %>%
  summarise(avg_rating = mean(Rating))
sorted_ratings <- average_rating %>%
  arrange(desc(avg_rating))
top_items <- head(sorted_ratings, 10)
average_rating <- average_rating %>%
  mutate(rating_range = cut(avg_rating, breaks = seq(0, 5, by = 1), labels = FALSE))
average_rating$rating_range <- factor(average_rating$rating_range)
ggplot(average_rating, aes(x = reorder(Clothing.ID, avg_rating), y = avg_rating, fill = rating_range)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("1" = "red", "2" = "orange", "3" = "yellow", "4" = "green", "5" = "blue"),
                    name = "Rating Range") +
  labs(title = "Average Ratings for Each Clothing ID",
       x = "Clothing ID",
       y = "Average Rating") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

In the basic analysis, we explored the dataset's structure and key variables, gaining insights into the age distribution of reviewers, the frequency distribution of ratings, and the distribution across product divisions, departments, and class names. Visualizations such as histograms and bar plots were utilized to provide a clear understanding of distribution patterns, while the calculation of average ratings for each clothing item and subsequent visualization allowed for the identification of top-rated items and analysis of rating distributions. Overall, this analysis provided foundational insights for further exploration and decision-making.

In the upcoming text analysis section, we'll delve into the textual content of customer reviews to explore themes, sentiments, and keywords. This will provide a comprehensive understanding of customer opinions and feedback. Analyzing the text of reviews enables us to uncover underlying trends and patterns, assisting retailers in better understanding customer needs, optimizing products and services, and enhancing overall customer satisfaction.

### c) Text Analysis

The text analysis section of this report focuses on extracting insights from customer reviews of women's clothing products. By leveraging natural language processing techniques, we aim to uncover key patterns and sentiments expressed in the review texts. Through the use of text mining and visualization tools, we delve into the language used by customers to describe their experiences with the products, shedding light on their preferences, sentiments, and priorities.

```{r}
library(tm)
library(tokenizers)
library(wordcloud)

review_text <- sample_data$Review.Text
review_text <- tolower(review_text)
review_text <- gsub("[^a-zA-Z\\s]", "", review_text)
tokens <- strsplit(review_text, "\\s+")
corpus <- Corpus(VectorSource(sample_data$Review.Text))
corpus <- tm_map(corpus, content_transformer(tolower))
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, removeNumbers)
corpus <- tm_map(corpus, removeWords, stopwords("en"))
corpus <- tm_map(corpus, function(x) unlist(tokenize_words(x)))
dtm <- DocumentTermMatrix(corpus)
mat <- as.matrix(dtm)
word_freq <- colSums(mat)
sorted_freq <- sort(word_freq, decreasing = TRUE)
head(sorted_freq,50)
```

Based on the results, the top 50 most frequent words in the reviews provide insights into the customers' sentiments and preferences. Here are some observations:

Positive Feedback: 
Words like "love", "great", "perfect", "beautiful", "really", "soft", "comfortable", "cute", "nice", "pretty", "flattering", and "good" indicate positive sentiments towards the clothing items. These words suggest that customers are generally satisfied with the products' quality, appearance, and comfort.

Fit and Size: 
Terms such as "fit", "size", "small", "large", "runs", and "fits" suggest that customers frequently mention the fit and sizing of the clothing items in their reviews. This indicates that fit and sizing are important factors influencing customers' purchasing decisions and overall satisfaction.

Specific Clothing Items: 
The word "dress" appears most frequently, indicating that dresses are a popular category among the reviewed clothing items. Other items like "top", "sweater", "jeans", and "shirt" also appear frequently, suggesting that customers frequently review various types of apparel.

Material and Quality: 
Words such as "fabric", "material", and "quality" suggest that customers pay attention to the materials used in the clothing items and value high-quality materials.
Color and Style: Terms like "color", "look", "look", "beautiful", "pretty", and "flattering" indicate that customers often comment on the appearance, style, and color options of the clothing items.

Overall, the analysis of the top 50 most frequent words provides valuable insights into customers' sentiments, preferences, and priorities when reviewing and purchasing clothing items online. These insights can help retailers better understand customer needs and preferences, identify areas for improvement, and make informed decisions about product offerings and marketing strategies.

```{r, echo=FALSE}
top_words <- data.frame(word = names(sorted_freq)[1:50], freq = sorted_freq[1:50])
barplot(top_words$freq, names.arg = top_words$word, las = 2, 
        main = "Top 50 Words by Frequency", xlab = "Word", ylab = "Frequency", col = "skyblue")
wordcloud(words = top_words$word, freq = top_words$freq, scale = c(3, 0.5), 
          min.freq = 10, random.order = FALSE, colors = brewer.pal(8, "Dark2"))
```

Through the analysis of customer review texts, we have gained a deeper understanding of their emotions, preferences, and evaluations of clothing products. First, by analyzing the top 50 most common words, we found that customers often give positive reviews on the quality, appearance, and comfort of the products, indicating their focus on these factors in purchasing decisions. Secondly, customers frequently mention the fit and size of clothing items, reflecting the importance of these factors in the purchasing process. In addition, specific types of clothing items such as dresses, tops, and sweaters are frequently mentioned in the reviews, reflecting customers' purchasing and evaluation habits for different types of clothing. Finally, customers also comment on the materials, colors, and styles of clothing items, providing valuable information for retailers to improve products and marketing strategies. In summary, text analysis of customer reviews provides valuable market insights for retailers to better meet customer needs and improve product and service quality.

Next up is sentiment analysis. We'll delve into the sentiment expressed in the customer reviews to gain insights into their overall satisfaction and opinions about the products.

### d) Sentiment Analysis

Sentiment analysis, also known as opinion mining, is a natural language processing technique used to determine the sentiment expressed in text data. In this section, we analyze the sentiment of customer reviews using sentiment analysis techniques. By quantifying the sentiment expressed in the reviews, we aim to gain insights into customers' opinions, attitudes, and emotions towards the products or services being reviewed. This analysis provides valuable information for businesses to understand customer satisfaction, identify areas for improvement, and make data-driven decisions to enhance the overall customer experience.

```{r}
library(tidyr)

tokens1 <- sample_data$Review.Text %>%
  tolower() %>%
  removePunctuation() %>%
  removeNumbers() %>%
  strsplit("\\s+") %>%
  unlist()
review_tokens <- data.frame(word = tokens1)
sentiment_scores <- review_tokens %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment_score = positive - negative)
sorted_sentiment <- sentiment_scores %>% arrange(desc(sentiment_score))
head(sorted_sentiment,50)
tail(sorted_sentiment,50)
str(sentiment_scores)
summary(sentiment_scores)
```

The sentiment scores dataset comprises 379 unique words, each assigned a sentiment score ranging from -32 to 167, indicating a broad spectrum of sentiment intensity. This diversity suggests that certain words may evoke stronger positive or negative sentiments than others, reflecting the richness and complexity of customer feedback.

Upon examining the summary statistics of the sentiment scores, we find that the average sentiment score across words is approximately 3.93, with a median of -1. This implies an overall inclination towards positive sentiment among the words analyzed. However, the distribution reveals variation, with most words clustered between -1 and 2. Such distribution suggests a tendency towards a positive sentiment, albeit with fluctuations across different words.

These insights underscore the nuanced nature of sentiment expressed in customer reviews, with certain words evoking stronger sentiments than others. Further exploration of how these sentiment scores correlate with other variables, such as product ratings or recommendation indicators, can provide deeper insights into the impact of sentiment on customer experience and feedback.

```{r, echo=FALSE}
barplot(sorted_sentiment$sentiment_score, names.arg = sorted_sentiment$word, las = 2, 
        main = "Sentiment Scores by Word", xlab = "Word", ylab = "Sentiment Score", col = "skyblue")
```

Upon examining the summary statistics of the sentiment scores, we find that the average sentiment score across words is approximately 3.93, with a median of -1. This implies an overall inclination towards positive sentiment among the words analyzed. However, the distribution reveals variation, with most words clustered between -1 and 2. Such distribution suggests a tendency towards a positive sentiment, albeit with fluctuations across different words.

Although we successfully conducted sentiment analysis on the text and obtained sentiment scores for words, we faced technical challenges preventing us from further conducting correlation analysis and regression analysis. This means that we couldn't delve deeper into exploring the relationship between sentiment scores and other variables such as product ratings or recommendation indicators. Nevertheless, we still gained valuable insights from the sentiment scores. These analyses indicate progress in identifying customer sentiments, yet a comprehensive understanding of how sentiment influences customer experience and feedback requires further research and exploration.

## 3. Conclusion and Summary

The analysis of the Women's Clothing E-Commerce dataset has provided valuable insights into consumer preferences and sentiments within the realm of online fashion retail. Through various stages of data preprocessing, basic analysis, text analysis, and sentiment analysis, we have gained a comprehensive understanding of customer behavior, product performance, and overall sentiment expressed in customer reviews.

During the data preprocessing stage, we prepared the dataset and conducted basic statistical analyses to understand the dataset's structure and distribution. This initial exploration provided foundational insights into customer demographics, review ratings, and product categories.

In the text analysis phase, we delved into the textual content of customer reviews to uncover prevalent themes, sentiments, and keywords. By analyzing the most frequent words in the reviews, we identified patterns indicating customer satisfaction, preferences for fit and size, and specific mentions of clothing items, materials, colors, and styles. This analysis shed light on customers' opinions and priorities when evaluating and purchasing clothing products online.

Furthermore, the sentiment analysis allowed us to quantify the sentiment expressed in customer reviews, providing insights into the overall satisfaction and opinions about the products. While technical challenges prevented us from conducting further correlation and regression analyses, the sentiment scores revealed an overall inclination towards positive sentiment among the words analyzed. This suggests a generally positive sentiment expressed by customers in their reviews, with fluctuations across different words.

In conclusion, the analysis of the Women's Clothing E-Commerce dataset has equipped retailers with valuable market insights to better understand customer needs, improve product offerings, and enhance overall customer satisfaction. By leveraging the findings from this analysis, retailers can make data-driven decisions to optimize product quality, marketing strategies, and customer engagement efforts, ultimately driving business success in the competitive landscape of e-commerce.